% Generated LaTeX version of the agreement
\documentclass[11pt]{article}
\usepackage{fontspec}
\setmainfont{DejaVu Sans}
\usepackage[margin=1in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{longtable}
\usepackage{setspace}
\onehalfspacing

\title{Web Portfolio Development \& Revenue Share Agreement}
\author{{Service Provider} --- {Client}}
\date{{Effective Date}}

\begin{document}
\maketitle

\section*{Parties}
\textbf{Service Provider:} \{\{Service Provider\}\}\\
\textbf{Client:} \{\{Client\}\}\\
\textbf{Effective Date:} \{\{Effective Date\}\}

\tableofcontents
\vspace{1em}

\section{Purpose}
This Agreement covers the creation, deployment, and maintenance of a simple mobile-friendly HTML/CSS/JavaScript portfolio website hosted on Cloudflare Pages with automated deployment from GitHub. It also defines the revenue share associated with sales made through this version of the Site.

\subsection{Intent of the Website}
The intended function of the Site is to provide the Client with:
\begin{itemize}
  \item A public portfolio showcasing artistic work.
  \item A soft web store used to market and sell \textbf{artist design services}, including but not limited to:
    \begin{itemize}
      \item Cover art design
      \item Promotional video production
      \item Music video storyboarding
      \item Graphic and visual design services
      \item Related artist-based creative services
    \end{itemize}
  \item A clean landing-page experience for social media profiles (Instagram, X/Twitter, TikTok, YouTube, etc.), including:
    \begin{itemize}
      \item Service descriptions
      \item Cover art samples
      \item Direct outbound links to all social media and external platforms
      \item Link-in-bio--optimized layout
    \end{itemize}
\end{itemize}

This Agreement applies \textbf{only} to this version of the Site. Any expansion beyond this intent (such as full e-commerce, subscription systems, or advanced interactive features) requires a new or revised agreement.

\section{Scope of Work}
Service Provider will design, build, and deploy a lightweight portfolio website consisting of:
\begin{itemize}
  \item Mobile-first HTML/CSS/JavaScript frontend
  \item Portfolio layout and media showcase
  \item Landing page optimized for social media integration and link-in-bio use
  \item Outbound links to Client social media accounts and external stores
  \item Integrated service inquiry or purchase flow (Google Forms, Stripe Checkout links, or both)
  \item Optional storefront-style sections for design services
  \item Basic payment link integration (non-custom)
  \item Light UX adjustments and ongoing minor updates
\end{itemize}

This is a minimal, static deployment intended for speed, reliability, and ease of maintenance.

\subsection{Technical Stack}
The Site will be built using:
\begin{itemize}
  \item \textbf{HTML / CSS / JavaScript}
  \item \textbf{Cloudflare Pages} (hosting, SSL, caching, CDN)
  \item \textbf{GitHub} (repository + automated deployments)
  \item \textbf{Google Forms} (for service inquiries/intake)
  \item \textbf{Payment Processor:} Stripe or PayPal (Stripe recommended for SKU, tax, and accounting simplicity)
\end{itemize}

\subsection{Social Media \& External Integration}
The Service Provider will implement:
\begin{itemize}
  \item Outbound social media links
  \item Link-card sections if requested
  \item Service summaries optimized for mobile
  \item Display of recent cover art or highlight works
  \item Clean navigation for users coming from bios or social platforms
\end{itemize}

\subsection{Repository \& Version Control}
\begin{itemize}
  \item Code will be stored in a GitHub repository owned by the Client (or jointly, if preferred).
  \item Cloudflare Pages will automatically build and deploy on each push to the designated branch.
  \item The repository is strictly for this version of the Site unless otherwise agreed.
\end{itemize}

\subsection{Design Revisions and Iteration}
The website design will be developed collaboratively based on the Client's needs and feedback. The Service Provider will offer reasonable revisions during the development phase prior to launch.

A ``revision'' is defined as a request to modify existing content, layout, styling, or visual elements that fall within the scope of the initial portfolio and landing-page design.

Revisions are included up until a formal \textbf{Launch Approval} or \textbf{Design Sign-Off}, whichever comes first. Once the Client provides written approval (email, message, or signature), the design is considered finalized.

Any redesigns, new page requests, major layout changes, or feature additions requested \emph{after} the sign-off point will be treated as out-of-scope and may require a separate agreement or additional fees.

\section{Revenue Share}
Client agrees to pay the Service Provider a \textbf{10\% revenue share} on all sales generated through this Site.

\subsection{Payment Structure}
Payments may be handled in either of these formats:
\begin{enumerate}
  \item \textbf{Platform-Integrated Splitting}: If Stripe or a similar platform supports automatic fee splitting, 10\% is routed directly to the Service Provider.
  \item \textbf{Manual Weekly Payouts}: If automatic splitting is unavailable, the Client will remit 10\% of \textbf{net sales} each week.
\end{enumerate}

\subsection{Net Sales Definition}
Net sales = gross sales collected \textbf{minus}:
\begin{itemize}
  \item Payment processor fees
  \item Refunds
  \item Chargebacks
\end{itemize}

\subsection{Transparency}
To maintain accuracy, Client will:
\begin{itemize}
  \item Provide view-only access to Stripe, PayPal, or Gumroad dashboards, \textbf{or}
  \item Send weekly exported sales summaries
\end{itemize}

\section{Ownership and Rights}
\subsection{Content Ownership}
\begin{itemize}
  \item Client owns all artwork, graphics, branding, and written content they provide.
  \item Service Provider owns custom code, templates, and technical configurations.
\end{itemize}

Client receives a \textbf{perpetual, non-exclusive license} to use the delivered website assets.

\subsection{Future Scaling}
If the Client later requires functionality beyond the scope of this project, such as:
\begin{itemize}
  \item A full e-commerce store
  \item Subscriptions or memberships
  \item Shopping cart system
  \item Digital product delivery
  \item Authentication or dashboards
  \item Custom backend or Workers API
  \item Major redesign or rebrand
  \item New pages or expanded sections
  \item Migration to a different tech stack
\end{itemize}
—these enhancements must be covered under a \textbf{new or amended agreement} with updated pricing and scope.

\section{Client Requirements}
Client must provide and maintain:

\subsection{Cloudflare Account}
\begin{itemize}
  \item Cloudflare account owned by Client
  \item Access granted to the Service Provider for:
    \begin{itemize}
      \item DNS configuration
      \item SSL/TLS
      \item Cloudflare Pages environment
      \item Basic routing/security adjustments
    \end{itemize}
\end{itemize}

\subsection{GitHub Access}
\begin{itemize}
  \item Client must provide Service Provider access to the GitHub repository used for the website
  \item Deployment settings as needed for Cloudflare Pages
\end{itemize}

\subsection{Payment Platform Accounts}
\begin{itemize}
  \item Client is responsible for:
    \begin{itemize}
      \item Stripe, PayPal, Gumroad, or alternate payment accounts
      \item Tax reporting
      \item Refunds
      \item Customer communication
      \item Legal or compliance obligations tied to their services
    \end{itemize}
\end{itemize}

\section{Maintenance}
\textbf{Included:}
\begin{itemize}
  \item Minor content updates
  \item Adding new portfolio items
  \item Social link updates
  \item Bug fixes
  \item Basic styling or UX tweaks
  \item Integration updates (payment links, Google Forms, etc.)
  \item Performance tuning and caching adjustments
\end{itemize}

\textbf{Not included (requires new agreement or service fees):}
\begin{itemize}
  \item Full redesign
  \item Major brand overhaul
  \item Custom or API integrations
  \item Expanded storefront features
  \item Backend development
  \item Cloudflare Workers apps beyond simple forms
  \item Migration to a different platform
  \item Major new features outside initial scope
\end{itemize}

\section{Term \& Termination}
\begin{itemize}
  \item Either party may terminate with \textbf{30 days written notice}.
  \item Failure to remit revenue share or provide transparency is grounds for immediate suspension or termination.
  \item Upon termination, the Client may continue using the delivered Site; revenue share applies only while this Agreement remains active.
\end{itemize}

\section{Liability}
Service Provider is not liable for:
\begin{itemize}
  \item Sales performance
  \item Third-party outages (Cloudflare, GitHub, Stripe, PayPal, etc.)
  \item Issues introduced by Client modifications
  \item Legal disputes tied to Client’s artwork or business
  \item Chargebacks, refunds, or payment disputes
  \item Tax compliance or financial liabilities
\end{itemize}

Service Provider will maintain the Site in good faith within defined scope.

\section{Entire Agreement}
This Agreement represents the full understanding between the parties for the development and revenue-sharing of the static portfolio website and supersedes all prior discussions.

\section*{Signatures}
\vspace{1em}
\noindent\begin{tabular}{p{0.45\textwidth} p{0.45\textwidth}}
\textbf{Service Provider} & \textbf{Client} \\
Name: \{\{Service Provider\}\} & Name: \{\{Client\}\} \\
Title: \{\{Service Provider Title\}\} & Title: \{\{Client Title\}\} \\
Signature: \rule{6cm}{0.4pt} & Signature: \rule{6cm}{0.4pt} \\
\end{tabular}

\end{document}
